\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-07-02 manuscript/main.tex
modified:   manuscript/main.tex

\begin{equation}
    Y_{it} = \beta_0 +  pre_2 + entry + \sum_{i=1}^3 post_i + \bf{\alpha} \bf{X}_{it} + \tau_{t} + \mu_i + \epsilon_{it}.   \label{eq:entry_effect}
\end{equation}

@@

This strategy is a significant change in Lianjia's business model, and it is expected to have a significant impact on the market. In addition to this, Lianjia also opened up the form of franchises and gradually started platform integration. To empirically measure the effect of platformization to the offline stores' operations, we first counted the number of all non-Lianjia stores on the Lianjia's Beke platform within a radius of 410 meters, which allowed us to generate a dummy variable $Treatment_{it}$ to represent whether or not there are any other affiliate stores within the platform in this neighborhood. To dynamically capture the varying effects, we generate $Treatmetn_{it} * year$ by producting the year dummy variable with the $Treatment_{it}$ and include them in our regression model. Since the ACN network was officially established at the end of 2018, we can generate a dummy variable equal to 1 if the year is greater than 2018. We then consider the following regression model:

\begin{equation}
    Y_{it}  = \beta_0 + \sum_{i=1}^5 Treatment_{it} * year + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}. \label{eq:acn_assessment}
\end{equation}

By focusing on 2017 as the baseline, we can empirically estimate the outcomes with greater precision and reliability, ensuring that our analysis accurately reflects the impact of Lianjia's strategy without the confounding effects of prior periods. Other settings are consistent with previous table \ref{tab:Dynamic} and the result is reported in Figure \ref{fig:dynamic_effect}.

@@

The empirical findings indicate that during the first year of consolidation, Lianjia's transaction revenue did not show a statistically significant difference from zero. However, from 2019 to 2021, the transaction revenue demonstrated a significant positive increase, ranging from 4.9\% to 2.6\%. Additionally, the consolidation of the platform had a significantly positive impact on the number of house tours, which increased by 3.9\% to 6.4\% from 2018 to 2022, with this trend continuing upward throughout the sample period. Furthermore, when comparing the effect of platform consolidation with the entry effect of offline stores, the data clearly show that the platformization effect is substantially more pronounced. This suggests that the platformization strategy is markedly more effective than the offline store entry strategy in generating revenue and attracting buyers in the market. These results underscore the superior efficacy of platform consolidation in enhancing market performance and provide compelling evidence for the strategic advantage of platformization over traditional offline expansion.

However, in terms of the transaction period, the platformization strategy does not exhibit a significant effect, indicating that platformization does not assist brokerages in facilitating better matching and negotiation between sellers and buyers. A similar pattern is observed in price concessions, suggesting that the platformization strategy does not contribute to reducing price concessions. While the platformization strategy is less effective in influencing individuals' decision-making processes compared to offline store entry, it proves more effective in increasing revenue and the number of house tours. This discrepancy highlights that the platformization strategy excels in attracting customers and generating revenue, but falls short in aiding the matching and negotiation process. These findings align with the intuition that platformization is more likely to draw customers and boost revenue, yet it is less effective in assisting buyers and sellers in reaching agreements.

>>>>

\begin{equation}
    Y_{it} = \beta_0 +  pre_2 + entry + \sum_{i=1}^3 post_i + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}.   \label{eq:entry_effect}
\end{equation}

@@

This strategy is a significant change in Lianjia's business model, and it is expected to have a significant impact on the market. In addition to this, Lianjia also opened up the form of franchises and gradually started platform integration. To empirically measure the effect of platformization on offline store operations, we first counted the number of all non-Lianjia stores on Lianjia's Beke platform within a radius of 410 meters. This allowed us to generate a dummy variable, $\text{Treatment}_{it}$, which equals one if the ratio $\frac{\text{Lianjia}}{\text{Beke}} < 0.8$ in this area and the year is 2018 or later. This ratio is selected because if Lianjia accounts for more than 80\% of the Beke's offline stores, the strategy's effect is negligible and only effective for Lianjia. To dynamically capture the varying effects, we generate a set of dummy variable $\text{post\_j\_treatment}_{it}$, where $j \in \{1, 2, 3\}$ and $\text{pre\_treatment}_{it}$ and include them in our regression model. We then consider the following regression model:

\begin{equation}
  \begin{aligned}
    Y_{it} & = \beta_0 + \beta_1 \text{prev\_treatment}_{it} + \beta_2 \text{\treatment}_{it} + \sum_{j=3}^5 \beta_{i} \text{post\_j\_treatment_{it}}+ \\
           & \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}. \label{eq:acn_assessment}
  \end{aligned}
\end{equation}

where our key independent variables are described above. Other settings are consistent with previous table \ref{tab:Dynamic} and the result is reported in Figure \ref{fig:dynamic_effect}.

@@

The empirical findings indicate that in the first year of the consolidation strategy, Lianjia's transaction revenue did not show a statistically significant difference. However, after the first year, the transaction revenue demonstrated a significant positive increase, ranging from 3\% to 6\%. Additionally, the platform consolidation had a significantly positive impact on the number of house tours, with effects following the same trend as the transaction revenue. Furthermore, when comparing the effect of platform consolidation with the entry effect of offline stores, the result indicates that the effect is substantially more pronounced and more continuous. These results underscore the superior efficacy of platform consolidation in enhancing market performance and provide compelling evidence for the strategic advantage of platformization over traditional offline expansion.

However, in terms of the transaction period, the platformization strategy does not exhibit a significant effect, indicating that platformization does not assist brokerages in facilitating better matching and negotiation between sellers and buyers. Moreover, in terms of the platform's consolidation effect on price concessions, we find that the effect is significant after the first period, with a 4.2\% increase in the first year after the treatment and a 7.1\% increase in the second year. However, the effect becomes insignificant after the third year. Overall, the results show that comparing with the offline store's entry effect, the platform's consolidation strategy can have more pronounced influence not only on effectiveness on trasaction but also on the overall revenue.

revise the paragraph to make it more economics and academic
( this is today's work )

While the platformization strategy is less effective in influencing individuals' decision-making processes compared to offline store entry, it proves more effective in increasing revenue and the number of house tours. This discrepancy highlights that the platformization strategy excels in attracting customers and generating revenue, but falls short in aiding the matching and negotiation process. These findings align with the intuition that platformization is more likely to draw customers and boost revenue, yet it is less effective in assisting buyers and sellers in reaching agreements.
